A new type of automated prover based on category theory

### 2022-08-27 paper.tex
fix overfull hbox warning (patch)
change table caption loc
add corresponding author info

\hfuzz=2pt
\special{dvipdfmx:config z 0} %% speed boost

@@

\title{A new type of automated prover based on category theory}
\author[1]{Zijian Wang\fnref{fn1}}
\ead{felix_wzj@yahoo.com}
\ead[url]{zijianfelixwang.github.io}

\fntext[fn1]{Author conducting the research, student of the Northeast Yucai School of P.R.China}

\affiliation[1]{organization={Northeast Yucai School},addressline={Shiji Rd. 41, Hunnan},city={Shenyang},postcode={110000},country={P.R.China}}
\maketitle

@@

\begin{keyword}
	automatic prover \sep theorem prover \sep algorithm \sep category theory \sep provers \sep statement prover
\end{keyword}

@@

\begin{table}
	\centering
	\label{table-1}
	\begin{tabular}{ccccccccccc}
		\toprule
		$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
		\midrule
		$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
		\bottomrule
	\end{tabular}
	\caption{The table for $\mathit{p}(\mathcal{N})$}
\end{table}

@@

\bibliographystyle{unsrt}
\bibliography{paper}

>>>>

\hfuzz=2pt
%% \special{dvipdfmx:config z 0} %% speed boost

%% The commands below, learnt from TeX stack exchange can cancel the hbox overfull warning...
\usepackage{etoolbox}
\makeatletter
\patchcmd\ps@pprintTitle
{\fi\fi\fi\fi}
{\fi\fi\fi\fi
	\afterassignment\fix@elsarticle\let\@tempa}
{}{\FailedToPatch}
\def\fix@elsarticle{\iffalse{\fi}\romannumeral-`0}
\makeatother

@@

\begin{frontmatter}
	\title{A new type of automated prover based on category theory}

	\author[1]{Shao Xinhui\corref{cor1}}
	\ead{shaoxinhui@mail.neu.edu.cn}

	\author[2]{Zijian Wang\fnref{fn2}}
	\ead{felix_wzj@yahoo.com}
	\ead[url]{zijianfelixwang.github.io}

	\cortext[cor1]{Corresponding author, guiding the first author through the process of the research, professor of the Northerneastern University.}

	\fntext[fn2]{Author conducting the research, student of the Northeast Yucai School of P.R.China}

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={Zhenxing St. 9-5, Heping District},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

@@

	\begin{graphicalabstract}
		\begin{figure}[h]
			\begin{tikzpicture}[commutative diagrams/every diagram]
				\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
				\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
				\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
				\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
				\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

				\path[commutative diagrams/.cd, every arrow, every label, dashed]
				(K3) edge node {$K_3$} (Kn)
				(Kn) edge node {} (K1)
				(Kn) edge node {$k_N$} (K0);
			\end{tikzpicture}
		\end{figure}
	\end{graphicalabstract}

	\begin{keyword}
		automatic prover \sep theorem prover \sep algorithm \sep category theory \sep provers \sep statement prover
	\end{keyword}
\end{frontmatter}

@@

\begin{table}
	\centering
	\label{table-1}
	\caption{The table for $\mathit{p}(\mathcal{N})$}
	\begin{tabular}{ccccccccccc}
		\toprule
		$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
		\midrule
		$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\bibliographystyle{elsarticle-num}
\bibliography{paper}
